VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper_conc.tex

\section{Conclusion}
\label{sect:conclusion}
%In this paper we propose a collocated backup service built on
%the top of a cloud cluster to reduce network traffic and infrastructure requirements.
The main contribution of this paper is a low-profile and VM-centric deduplication scheme to 
maximize fault isolation while delivering competitive deduplication efficiency using
a small amount of system resource.
Evaluation using  this scheme strikes a tradeoff and restricted cross-VM duplicate detection
can accomplish 96.33\% or 96.9\% of what complete global
deduplication can do, and the VM-centric
approximate snapshot deletion effectively manages deleted chunks with a 
low-resource usage.  The availability of snapshots increases substantially when
adding more replication for popular cross-VM chunks and packaging chunks from the same 
VM in one file system block. The analysis shows that the replication degree
for the popular data set between 6 and 9 is good enough when the replication degree
for other data blocks is 3.
%Currently we are studying how the

>>>>

\section{Conclusion}
\label{sect:conclusion}
%In this paper we propose a collocated backup service built on
%the top of a cloud cluster to reduce network traffic and infrastructure requirements.
The main contribution of this paper is a low-profile and VM-centric deduplication scheme to 
maximize fault isolation while delivering competitive deduplication efficiency using
a small amount of system resource.
Evaluation using  this scheme strikes a tradeoff and restricted cross-VM duplicate detection
can accomplish up to 96.58\% of what complete global
deduplication can do, and the approximate snapshot deletion effectively manages deleted chunks with a 
low-resource usage.  The availability of snapshots increases substantially when
adding more replication for popular cross-VM chunks and packaging chunks from the same 
VM in one file system block. The analysis shows that the replication degree
for the popular data set between 6 and 9 is good enough when the replication degree
for other data blocks is 3.
%Currently we are studying how the
